Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-09-12 paper/proof/13636_2018_138_MOESM1.tex
proofread up to page 2

In order to preserve energy and allow for perfect reconstruction,
the Gammatone wavelet filter bank must satisfy the inequalities
\[
1-\varepsilon\leq\vert\boldsymbol{\hat{\phi}}(\omega)\vert+\sum_{\gamma}\vert\boldsymbol{\hat{\psi}}(2^{\gamma}\omega)\vert+\vert\boldsymbol{\hat{\psi}}(-2^{\gamma}\omega)\vert\leq1
\]
for all frequencies $\omega$ in the audible range, where $\varepsilon$ is a small margin
\cite{Anden2014}. 
Let $\xi_{\mathrm{s}}$ be the sampling rate of the audio signal $\boldsymbol{x}(t)$ at hand.
Satisfying the equation above near the Nyquist
frequency $\omega=\frac{1}{2}\xi_{\mathrm{s}}$ can be achieved by placing the log-frequency
$\log_{2}\xi$ of the first (topmost) wavelet in between the log-frequency
$\log_{2}(\xi\times2^{-1/Q})$ of the second wavelet and the log-frequency
$\log_{2}(\xi_{\mathrm{s}}-\xi)$ of the mirror of the first wavelet. We obtain
the equation
\[
\log_{2}\xi-\log_{2}(\xi\times2^{-1/Q})=\log_{2}(2\pi-\xi)-\log_{2}\xi,
\]

of which we deduce the identity
\[
\xi=\dfrac{2\pi}{1+2^{1/Q}}.
\]
For $Q=1$, this yields a center frequency of $\xi=\frac{2\pi}{3}$.
For greater values of $Q$, the center frequency $\xi$ tends towards
$\pi$.

>>>>

In order to preserve energy and allow for perfect reconstruction,
the Gammatone wavelet filter bank must satisfy the inequalities
\[
1-\varepsilon\leq\vert\boldsymbol{\hat{\phi}}(\omega)\vert+\sum_{\gamma}\vert\boldsymbol{\hat{\psi}}(2^{\gamma}\omega)\vert+\vert\boldsymbol{\hat{\psi}}(-2^{\gamma}\omega)\vert\leq1
\]
for all frequencies $\omega$ in the audible range, where $\varepsilon$ is a small margin
\cite{Anden2014}. 
Let $\xi_{\mathrm{s}}$ be the sampling rate of the audio signal $\boldsymbol{x}(t)$ at hand.
Satisfying the equation above near the Nyquist
frequency $\omega=\frac{1}{2}\xi_{\mathrm{s}}$ can be achieved by placing the log-frequency
$\log_{2}\xi$ of the first (topmost) wavelet in between the log-frequency
$\log_{2}(\xi\times2^{-1/Q})$ of the second wavelet and the log-frequency
$\log_{2}(\xi_{\mathrm{s}}-\xi)$ of the mirror of the first wavelet. We obtain
the equation
\[
\log_{2}\xi-\log_{2}(\xi\times2^{-1/Q})=\log_{2}(\tfrac{1}{2}\xi_{\mathrm{s}}-\xi)-\log_{2}\xi,
\]

of which we deduce the normalized identity
\[
\dfrac{\xi}{\xi_\mathrm{s}}=\dfrac{1}{1+2^{1/Q}}.
\]
For $Q=1$, this yields a center frequency of $\xi=\frac{1}{3}\xi_{\mathrm{s}}$.
For greater values of $Q$, the center frequency $\xi$ tends towards the Nyquist frequency $\frac{1}{2}\xi_{\mathrm{s}}$.
